Comets in star clusters: I. Dynamics of free-floating comets

### 2018-01-17 paper.tex
update

\cite{Spurzem:2009aa} investigated the instabilities of planetary systems in star clusters, and the ejection process of planets from their host system.  \cite{Wang:2015ab}  studied the survival rate of these ejected free-floating planets (FFPs). In this paper, We will consider both the recaptured FFPs and planets ejected out of star cluster.

@@

Simulations are run using a version of \nb\ \citep{Wang:2015ab} that is adjusted to suit the purpose of our simulations. Stellar evolution and binary evolution are implemented following the prescriptions of Cambridge stellar evolution package \citep{Eggleton:1989aa, Hurley:2000aa}.

We have adjusted the \nb\ package to be able to integrate large numbers of comets. The mass of comets is many orders of magnitude smaller than that of stars, and the comets can therefore be safely treated as test particles. Star-comet binaries are excluded from KS scheme. When calculated the gravitational interaction from other particles to a certain star, comets are ignored. Also, we disabled the stellar evolution of comets. %\textbf{GPU part to be discussed.}
As comets can be safely treated as massless particles, the choice for total number of comets, $\ncomets$ will not affect our results, other than statistically. The results can be easily scaled up to realistic values of $\ncomets$. 
All particles (stars, comets, or multiple systems) are considered as bound to the star clusters when they are within two tidal radii of the cluster centre. Otherwise, they are considered to have escaped from the star cluster.

Binary systems, which can be either star-star or star-comet systems. We do not consider comet-comet binaries, as these do not occur when considering massless particles. For each pair of bodies in the system we mutual binding energy. If this mutual binding energy is negative (i.e., we have identified a candidate binary), we proceed as follows: (1) if both bodies have mass, then they only form a bound binary if they are each other's mutual nearest neighbours with mass;, and (2) if only one body has mass, then the two bodies only form a binary if the body with mass is the nearest body with mass of the massless particle. We then obtain the orbital elements of each binary. We consider only binaries with semi-major axes less than ~ 1pc, which corresponds to the stability limit in the Galactic field. Note that one star can have multiple comet companions. Also, binary stars can have one or more comet companions in S-formation or P-formation.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{time_used.pdf}
  \caption{Time used in simulations with same number of single star 128k, but different number of free-floating comets from 12.8k to 128k.}
  \label{fig:time_used}
\end{figure}

@@

Our simulations are carried out on a workstation with an Intel CPU (i7-5960X CPU @ 3.00GHz) and two NVIDA GPU cards (GeForce GTX 980 Ti).

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{v2_r.png}
  \caption{The velocity and distance distribution of particle in the simulation, $N_{star} = N_{comet} = 128k$, Q = 0.5.}
  \label{fig:v2_r}
\end{figure}

We evolve star cluster models that correspond to large open clusters or small globular clusters. Our initial conditions are summarised in Table~\ref{table:initial}. The positions and velocities of all stars are drawn from the \cite{Plummer:1911aa} model in virial equilibrium with a virial radius of $\rvir=5 \sim 20$~pc. Stellar masses are drawn from the Kroupa (2001) initial mass function (IMF) in the range $0.08-20\msun$. We do not include primordial binaries, nor do we include primordial mass segregation. One of the $v^{2} \sim r$ plots can be seen in Figure \ref{fig:v2_r}. Each model is embedded in a standard solar neighbour tidal field, see Table~\ref{table:tidal}.

\begin{table*}
\caption{Initial conditions for our default model.  \label{table:initial}}
\begin{tabular}{ll}
\hline
\hline
Quantity & Value \\
\hline
Number of stars & $ \nna  \sim 12.8k $ large open cluster \\
 & $\nnc  128k$  small globular cluster \\

Stellar IMF &  Kroupa(2001), extended to Brown Dwarf regime\\ %KZ(20) = 6 
Virial radius & $\rvir=20$~pc (probably following a mass-radius relationship) \\
Dynamical model & \cite{Plummer:1911aa} \\
Stellar evolution &  Enable mass loss \\ %P.P. Eggleton, M.J. Fitchett \& C.A. Tout (1989) Ap.J. 347, 998.
Tidal field & no tidal force\\ %KZ(14) = 0 
\hline
Comet mass & Test particles \\
Comet-to-star-ratio & $\ratio=\ncomets/N= 1$ \\
Comet spatial distribution & Statistically identical to stars \\
Comet velocity distributions & $\qe=0.5$ (in virial equilibrium with stars) \\
	& $\qc=0.9$ (hot) \\
\hline
\hline
\end{tabular}
\end{table*}

@@

\begin{table*}
\caption{standard solar neighbour tidal field \label{table:tidal}}
\begin{tabular}{ll}
\hline
\hline
POINT-MASS MODEL (NB unit) \\
\hline
  MG  & $1.5 \times 10^8$  \\
  RG  &  $7.8 \times 10^3$  \\
  OMEGA & $1.8 \times 10^{-2}$ \\
  RTIDE & $11.5$  \\
  RBAR & $1.09$ \\
\hline
DISK MODEL \\
\hline
    MD &  $8.1 \times10^7$  \\
    A &  $3.7 \times10^3$  \\
    B &  $4.6 \times10^2$\\
\hline
SCALED ORBIT\\
\hline
    RG &  $7.78 \times 10^3$,  0.00,  0.00  \\
    VG &   0.00,  $1.41 \times10^2$,  0.00  \\
    $V_{0}$ &   $0.00$\\
\hline
\hline
\end{tabular}
\end{table*}

The population of $\ncomets$ free-floating planets is constructed independently of that of the stars. Their positions are also drawn from the \cite{Plummer:1911aa} model with a virial radius identical to that of the stellar mass distribution. Their velocity distribution is also constructed from the \cite{Plummer:1911aa} model, with a different $Q$ than the stars in order to investigate the evolution of different systems. We investigate the evolution of comet populations in different virial states:  $\qe=0.5$ (in equilibrium with the stellar population), and $\qh=0.9$ (hot). We did not discuss the case of $Q < 0.5$ because when comets are liberated from their host stars (through ejection or external perturbations), their kinetic energy is beyond the stars's escape velocity, and the comet population is therefore expected to be somewhat hotter than the stellar population. The models with $\qe$ represent comet ejections with negligible escape velocities, while the $\qh$ models represent high-velocity comet escapers.

Each model is integrated for 1000 $N$-body time units, corresponds to roughly 250 and 78.6 Myr.

@@

@@

Star cluster evolution is dominated by its stellar contents. For our model  $\nna$ and $\nnc$ star clusters, the initial crossing time are 0.93 and 0.22 Myr, respectively.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{lagrALL.pdf}
  \caption{Lagrangian radii for all particles, considering the tiny small mass of massless particles, it is also Lagrangian radii for all stars.}
  \label{fig:lagrALL}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{lagrMASSLESS.pdf}
  \caption{Lagrangian radii for all massless particles.}
  \label{fig:lagrMASSLESS}
\end{figure}

We calculate the time-dependent Lagrangian radii for both the stellar population, $\lags(t)$ and for the cometary population $\lagc(t)$, see figure \ref{fig:lagrALL} and figure \ref{fig:lagrMASSLESS}.

Discuss evolution of the comet population here. Lagrangian radii, number of comets escaping, escape rates, comet-to-star ratios. Refer to \cite{Wang:2015ab}.

The stability of such star-comet systems is a strong function of the orbital semi-major axis \citep[e.g.,][]{Zheng:2015aa}.

\subsection{Re-capture of comets}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{Ns_c.png}
  \caption{Number evolution of star-comet binaries. The simulation starts with 128k single stars and 128k free-floating comets.}
  \label{fig:Ns_c}
\end{figure}

\textbf{NOTE: we do not have enough captured comets to give statistical results for this section}
While most free-floating comets escape, a small fraction is captured by stars. Describe how this fraction depends on time and on the other initial properties of the star cluster. Discuss the lifetime of such a captured object, and relate to escaping star-comet systems.

Orbital parameter discussions here. Semi-major axis distributions are possibly log-normal or possibly log-flat. The distribution is probably bi-model: smaller-$a$ and larger-$a$. The ones with smaller $a$ are the results of three-body interactions in star clusters. The ones with larger $a$ are all escapers, and they are formed from a capture process during their escape.

Eccentricity distributions. The eccentricity distributions will likely resemble the thermal eccentricity distribution, $f(e)=2e$ for $0\leq e < 1$ \citep{heggie:1975aa}. Equation descriptions for these: probably power laws with upper and lower limits. Correlations between semi-major axis and eccentricity distributions, possibly with a two-dimensional distribution function.

A test simulation with our new code shows the result as figure \ref{fig:Ns_c}. 
%Discuss perihelion distributions, to check how they might interact with existing planetary systems.

@@

\subsection{Exchange of cometary material}

\textbf{NOTE: $X_{L}$ is mush smaller than $1\%$}

In this section we make analytical estimates for the level at which comets are exchanged between stars in a star cluster. Let $N_S$ be the number of stars in a star cluster, and $N_C$ be the average number of comets orbiting each star. Suppose also that each star loses a fraction $x_L$ of its comets, either through ejection or as a result of external perturbations. The total number of liberated comets in the cluster is then $x_LN_SN_C$. Suppose a fraction $x_R$ is of these free-floating comets is recaptured. Then the total number of recaptured comets is $x_Rx_LN_SN_C$, and each star captures $x_Rx_LN_C$ comets on average. This includes stars that remain bound to the cluster and stars that escape into the Galactic field. On average, the fraction of re-captured comets per star (relative to the remaining comets orbiting that star) is then $x_Rx_L(1-x_L)^{-1}$, which approximates to $x_Rx_L$ when $x_L\ll 1$.

Suppose that each star loses $x_R=10\%$ of its comets, and that $x_L=1\%$ of the comets are re-captured. Then, on average, $0.1\%$ of the comets orbiting each star is foreign. When applying this simple model to our solar system, and use $N_C=10^{11}$, the total number of re-captured comets is of order a billion.

This simplistic calculation is merely an approximation, as we have ignored the dependence of $x_L$ and $x_R$ on the star cluster environment and on time, and also the dependence of $x_L$ on the architecture of the planetary system.

@@

Summary of the project. Context, why we do it, what we do, how we do it. We find that 
%
\begin{itemize}
\item Comet escape rates and general dependence on initial conditions.
\item Comet capture rates
\item Orbital parameter distributions of captured comets
\item We predict that typically 0.1\% of the comets in our Solar system and in Oort clouds of other stars are re-captured, and have their origin in other planetary systems.

Future works.

In this work we have considered the dynamical evolution of comets in star clusters after these comets have been ejected from their host systems. In our next paper (Shu et al., in prep.) we will study the more realistic situation in which planets are initialised on circumstellar orbits. These simulations will naturally account for the release of comets from their host systems at appropriate times, appropriate positions in the star cluster, and with realistic ejection velocities.

@@

\end{itemize}

@@

%-------------------------------------------------------------------
%   bibliography
%-------------------------------------------------------------------
\clearpage
\phantomsection
\bibliographystyle{apj} 
\bibliography{Qi}

@@

>>>>

\cite{Spurzem:2009aa} investigated the instabilities of planetary systems in star clusters, and the ejection process of planets from their host system.  \cite{Wang:2015ab}  studied the survival rate of these ejected free-floating planets (FFPs). In this paper, We will consider the free-floating comets born in the cluster field and study their dynamical evolution and captured possibility.

@@

Simulations are run using a new version of \nb\ \citep{Wang:2015ab} which is adjusted to suit the purpose of our simulations. Stellar evolution and binary evolution are implemented following the prescriptions of Cambridge stellar evolution package and the improvements \citep{Eggleton:1989aa, Hurley:2000aa, Hurley:2005aa, Belczynski:2007aa}.

We have adjusted the \nb\ package to be able to integrate large numbers of comets. The mass of comets is ten times orders of magnitude smaller than that of stars, and the comets can therefore be safely treated as test particles. Star-comet binaries are excluded from KS scheme. When calculated the gravitational interaction from other particles to a certain star, comets are ignored. %\textbf{GPU part to be discussed.}
As comets can be safely treated as massless particles, the choice for total number of comets, $\ncomets$ will not affect our results, other than statistically. The results can be easily scaled up to realistic values of $\ncomets$. 
%All particles (stars, comets, or multiple systems) are considered as bound to the star clusters when they are within two tidal radii of the cluster centre. Otherwise, they are considered to have escaped from the star cluster.

Binary systems, which can be either star-star or star-comet systems. We do not consider comet-comet binaries, as these do not occur when considering massless particles. For each pair of bodies in the system we mutual binding energy. If this mutual binding energy is negative (i.e., we have identified a candidate binary), we proceed as follows: (1) if both bodies have mass, then they only form a bound binary if they are each other's mutual nearest neighbours with mass;, and (2) if only one body has mass, then the two bodies only form a binary if the body with mass is the nearest body with mass of the massless particle. We then obtain the orbital elements of each binary. We consider only binaries with semi-major axes less than one parsec, which corresponds to the stability limit in the Galactic field. 
%Note that one star can have multiple comet companions. Also, binary stars can have one or more comet companions in S-formation or P-formation.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{time_used.pdf}
  \caption{Time used in the 10 N-body unit test simulations with same number of single star 64k/128k, but different number of free-floating comets from 0 to 64k/128k.}
  \label{fig:time_used}
\end{figure}

@@

Our simulations are carried out on a workstation with an Intel CPU (i7-5960X CPU @ 3.00GHz) and one/two NVIDA GPU cards (GeForce GTX 980 Ti).

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{v2_r.png}
  \caption{The velocity and distance distribution of particle in the simulation, $N_{s} = N_{c} = 128$k, Q = 0.5.}
  \label{fig:v2_r}
\end{figure}

We evolve star cluster models that correspond to large open clusters or small globular clusters. Our initial conditions are summarised in Table~\ref{table:initial}. 
The positions and velocities of all stars are drawn from the \cite{Plummer:1911aa} model in virial equilibrium with a virial radius of $\rvir=5 \sim 20$~pc. Stellar masses are drawn from the Kroupa (2001) initial mass function (IMF) in the range $0.08 \sim100\msun$. 
We do not include primordial binaries, nor do we include primordial mass segregation. One of the $v^{2} \sim r$ plots can be seen in Figure \ref{fig:v2_r}. The tidal force is currently disabled. %Each model is embedded in a standard solar neighbour tidal field, see Table~\ref{table:tidal}.

\begin{table*}
\caption{Initial conditions for our default model.  \label{table:initial}}
\begin{tabular}{ll}
\hline
\hline
Quantity & Value \\
\hline
Number of stars &  12800 \\
Stellar IMF &  Kroupa(2001), 0.08-100 solar masses\\ %KZ(20) = 6 
Virial radius & $\rvir=20$~pc \\ % (probably following a mass-radius relationship) \\
Dynamical model & \cite{Plummer:1911aa} \\
Stellar evolution &  Enable mass loss \\ %P.P. Eggleton, M.J. Fitchett \& C.A. Tout (1989) Ap.J. 347, 998.
Tidal field & no tidal force\\ %KZ(14) = 0 
\hline
Comet mass & Test particles \\
Comet-to-star-ratio & $\ratio=\ncomets/N= 1$ \\
Comet spatial distribution & Statistically identical to stars \\
Comet velocity distributions & $Q=0.5$ (in virial equilibrium with stars) \\
	%& $\qc=0.9$ (hot) \\
\hline
\hline
\end{tabular}
\end{table*}

@@

The population of $\ncomets$ free-floating planets is constructed independently of that of the stars. Their positions are drawn from the \cite{Plummer:1911aa} model with a virial radius identical to that of the stellar mass distribution. Their velocity distribution is also constructed from the \cite{Plummer:1911aa} model with $Q=0.5$. The model is integrated for 70000 $N$-body time units.%, corresponds to roughly 250 and 78.6 Myr.

% different $Q$ than the stars in order to investigate the evolution of different systems. We investigate the evolution of comet populations in different virial states:  $\qe=0.5$ (in equilibrium with the stellar population), and $\qh=0.9$ (hot).

%We did not discuss the case of $Q < 0.5$ because when comets are liberated from their host stars (through ejection or external perturbations), their kinetic energy is beyond the stars's escape velocity, and the comet population is therefore expected to be somewhat hotter than the stellar population. The models with $\qe$ represent comet ejections with negligible escape velocities, while the $\qh$ models represent high-velocity comet escapers.

@@

We have carried out some long simulations as shown in Table~\ref{table:details}.

\begin{table*}
\caption{The long simulation details. $N_{s}$ number of stars, $ N_{c}$ number of comets, $B\%$ primordial star-star binaries fraction,$b\%$ primordial star-comet binaries fraction, NBt simulated N-body time, $T_{cal}$ real time used for calculation in unit of seconds. \label{table:details}}
\begin{tabular}{llllllll}
\hline
\hline ID        &   $N_{s}$    &   $N_{c}$ &  $B\%$  &    $b\%$    &      NBt      & $T_{cal}$        \\
\hline A5      &   12.8k     &   12.8k     &    0        &    0             &      70000  &      100350      \\
\hline E2      &   12.8k     &   12.8k     &    10      &    0             &      70000  &      180370      \\
\hline
\hline
\end{tabular}
\end{table*}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{PE.pdf}
  \caption{Calculation time costed in different processes.}
  \label{fig:PE}
\end{figure}

A reasonable calculation cost distribution of simulation should be like Figure  \ref{fig:PE}. This figure shows the distribution of calculation time cost in  the simulation A5. The time for irregular and regular force calculation always dominate at the beginning, while the time for adjust process keep growing as simulation goes.

@@

%Star cluster evolution is dominated by its stellar contents. For our model  $\nna$ and $\nnc$ star clusters, the initial crossing time are 0.93 and 0.22 Myr, respectively.
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth,height=!]{lagrComparing.pdf}
  \caption{Lagrangian radii for all particles, considering the tiny small mass of massless particles, it is also Lagrangian radii for all stars.}
  \label{fig:lagrComparing}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth,height=!]{lagr2000st.pdf}
  \caption{Only show the first 2000 N-body time.}
  \label{fig:lagr2000st}
\end{figure}

We calculate the time-dependent Lagrangian radii for both the stellar population and for the cometary population. At the begging of the simulation, the massive particles go through a gravitational resonance around the cluster centre while the massless particles do not, see figure \ref{fig:lagr2000st}.  Only the massive particles can have the three-body close encounter and then be ejected from the cluster centre, so at the late time, the same mass ratio Lagrangian radii lines for the massive particles are clearly higher than that of massless particles, shown as figure \ref{fig:lagrComparing}.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{avmass.pdf}
  \caption{Average mass of all particles in different Lagrangian radii shells.}
  \label{fig:avmass}
\end{figure}

Figure  \ref{fig:avmass} shows how the average mass of particles change with time in these Lagrangian radii shells. The average mass in the core region can be as high as ten times of that in the outside regoin.

%Discuss evolution of the comet population here. Lagrangian radii, number of comets escaping, escape rates, comet-to-star ratios. Refer to \cite{Wang:2015ab}.

%The stability of such star-comet systems is a strong function of the orbital semi-major axis \citep[e.g.,][]{Zheng:2015aa}.

\subsection{Captured of comets}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{Ns_c.png}
  \caption{Number evolution of star-comet binaries. The simulation starts with 12.8k single stars and 12.8k free-floating comets.}
  \label{fig:Ns_c}
\end{figure}

%\textbf{NOTE: we do not have enough captured comets to give statistical results for this section}
While most free-floating comets escaping, a small fraction is captured by free-floating stars. Only single digit free-floating comets are captured by a certain star at a solar age, see as figure \ref{fig:Ns_c}. Increasing the primodial star binaries fraction will not give significant difference, see figure \ref{fig:Ns_c10}
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth,height=!]{Ns_c10}
  \caption{Number evolution of star-comet binaries. The simulation starts with 12.8k stars with 10\% primordial binaries and 12.8k free-floating comets.}
  \label{fig:Ns_c10}
\end{figure}

We can estimate the probability of capturing comets for a single star by counting the number of single stars, single comets and star-comet binaries, $p = \frac{N_{s-c}}{N_{star}N_{comet}} $. From simulation we have $ N_{star} = N_{comet} = $12.8k and $<N_{s-c}> \sim 1$, so $ p \sim10^{-8}$.

Considering the total mass of Oort Cloud comets is about 5 Earth masses \citep{Morbidelli:2005aa}, we expect total mass of free-floating comets in the embedded cluster(where the Sun was originally born) is around $10^{3}$ solar masses. The current micro-lensing observations are sensitive to object mass down to earth mass, the observation of cometary object in star cluster is still too difficult in the near future.

%Describe how this fraction depends on time and on the other initial properties of the star cluster. Discuss the lifetime of such a captured object, and relate to escaping star-comet systems.

%Orbital parameter discussions here. Semi-major axis distributions are possibly log-normal or possibly log-flat. The distribution is probably bi-model: smaller-$a$ and larger-$a$. The ones with smaller $a$ are the results of three-body interactions in star clusters. The ones with larger $a$ are all escapers, and they are formed from a capture process during their escape.

%Eccentricity distributions. The eccentricity distributions will likely resemble the thermal eccentricity distribution, $f(e)=2e$ for $0\leq e < 1$ \citep{heggie:1975aa}. Equation descriptions for these: probably power laws with upper and lower limits. Correlations between semi-major axis and eccentricity distributions, possibly with a two-dimensional distribution function.

%A test simulation with our new code shows the result as figure \ref{fig:Ns_c}. 
%Discuss perihelion distributions, to check how they might interact with existing planetary systems.

@@

@@

%Summary of the project. Context, why we do it, what we do, how we do it. We find that 
%
%\begin{itemize}
%\item Comet escape rates and general dependence on initial conditions.
%\item Comet capture rates
%\item Orbital parameter distributions of captured comets
%\item We predict that typically 0.1\% of the comets in our Solar system and in Oort clouds of other stars are re-captured, and have their origin in other planetary systems.

%Future works.

In this work we have considered the dynamical evolution of comets in star clusters. To simulate such system, we developed a new version of N-body code. We found the different dynamical evolution behavior of free-floating comets than that of stars in the cluster. We expect several thousands solar masses equivalent free-floating comets in the embedded star cluster. We still need more simulations and observations to give preciser results.
In our next paper (Shu et al., in prep.) we will study the more realistic situation in which planets are initialised on circumstellar orbits. 
%These simulations will naturally account for the release of comets from their host systems at appropriate times, appropriate positions in the star cluster, and with realistic ejection velocities.

@@

%\end{itemize}

@@

%-------------------------------------------------------------------
%   bibliography
%-------------------------------------------------------------------
\clearpage
%\phantomsection\
%\bibliographystyle{apj} 
\bibliographystyle{mn2e} 
\bibliography{Qi}

@@

%
%\begin{table*}
%\caption{standard solar neighbour tidal field \label{table:tidal}}
%\begin{tabular}{ll}
%\hline
%\hline
%POINT-MASS MODEL (NB unit) \\
%\hline
%  MG  & $1.5 \times 10^8$  \\
%  RG  &  $7.8 \times 10^3$  \\
%  OMEGA & $1.8 \times 10^{-2}$ \\
%  RTIDE & $11.5$  \\
%  RBAR & $1.09$ \\
%\hline
%DISK MODEL \\
%\hline
%    MD &  $8.1 \times10^7$  \\
%    A &  $3.7 \times10^3$  \\
%    B &  $4.6 \times10^2$\\
%\hline
%SCALED ORBIT\\
%\hline
%    RG &  $7.78 \times 10^3$,  0.00,  0.00  \\
%    VG &   0.00,  $1.41 \times10^2$,  0.00  \\
%    $V_{0}$ &   $0.00$\\
%\hline
%\hline
%\end{tabular}
%\end{table*}
%
%\subsection{Exchange of cometary material}
%
%\textbf{NOTE: $X_{L}$ is mush smaller than $1\%$}
%
%In this section we make analytical estimates for the level at which comets are exchanged between stars in a star cluster. Let $N_S$ be the number of stars in a star cluster, and $N_C$ be the average number of comets orbiting each star. Suppose also that each star loses a fraction $x_L$ of its comets, either through ejection or as a result of external perturbations. The total number of liberated comets in the cluster is then $x_LN_SN_C$. Suppose a fraction $x_R$ is of these free-floating comets is recaptured. Then the total number of recaptured comets is $x_Rx_LN_SN_C$, and each star captures $x_Rx_LN_C$ comets on average. This includes stars that remain bound to the cluster and stars that escape into the Galactic field. On average, the fraction of re-captured comets per star (relative to the remaining comets orbiting that star) is then $x_Rx_L(1-x_L)^{-1}$, which approximates to $x_Rx_L$ when $x_L\ll 1$. 
%
%Suppose that each star loses $x_R=10\%$ of its comets, and that $x_L=1\%$ of the comets are re-captured. Then, on average, $0.1\%$ of the comets orbiting each star is foreign. When applying this simple model to our solar system, and use $N_C=10^{11}$, the total number of re-captured comets is of order a billion.
%
%This simplistic calculation is merely an approximation, as we have ignored the dependence of $x_L$ and $x_R$ on the star cluster environment and on time, and also the dependence of $x_L$ on the architecture of the planetary system.
